Stellar and Planetary Properties of \KT\ Campaign 1 Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-04-16 table_fpp.tex
updated FPP calculations

201208431.01 & $0.51$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $7.0\times10^{-4}$ & $0.21$ & $7.0\times10^{-4}$ & Planet  \\
 \color{red} 201257461.01  & \color{red}  $0.59$  & \color{red}   -  & \color{red}  $8.8\times10^{-3}$  & \color{red}  $0.940$  & \color{red}  $0.051$  & \color{red}  $0.17$  & \color{red}  $1.000$  & \color{red}  FP \\

@@

201338508.01 & $0.63$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $3.2\times10^{-3}$ & $0.21$ & $3.2\times10^{-3}$ & Planet  \\
201338508.02 & $0.33$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $1.8\times10^{-4}$ & $0.22$ & $1.8\times10^{-4}$ & Planet  \\
201367065.01 & $0.15$ &  - & $0.717$ & $< 10^{-4}$ & $0.044$ & $0.07$ & $0.761$ & Planet\tablenotemark{c}  \\
201367065.02 & $0.67$ &  - & $3.2\times10^{-3}$ & $< 10^{-4}$ & $4.2\times10^{-3}$ & $0.17$ & $7.4\times10^{-3}$ & Planet\tablenotemark{c}  \\
201384232.01 & $0.44$ &  - & $1.2\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.16$ & $1.4\times10^{-4}$ & Planet  \\
201393098.01 & $0.52$ &  - & $1.6\times10^{-3}$ & $< 10^{-4}$ & $5.5\times10^{-4}$ & $0.19$ & $2.2\times10^{-3}$ & Planet  \\

@@

201445392.01 & $0.26$ &  - & $1.3\times10^{-3}$ & $< 10^{-4}$ & $0.012$ & $0.19$ & $0.013$ & Candidate  \\
201445392.02 & $0.18$ &  - & $0.023$ & $< 10^{-4}$ & $0.254$ & $0.21$ & $0.277$ & Candidate  \\
201465501.01 & $0.68$ &  - & $0.491$ & $0.022$ & $9.1\times10^{-3}$ & $0.20$ & $0.522$ & Candidate  \\
201505350.01 & $2.69$ &  - & $0.583$ & $< 10^{-4}$ & $0.024$ & $0.07$ & $0.607$ & Planet\tablenotemark{d}  \\
201505350.02 & $0.70$ &  - & $0.034$ & $< 10^{-4}$ & $2.3\times10^{-4}$ & $0.07$ & $0.034$ & Planet\tablenotemark{d}  \\
201546283.01 & $0.15$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.06$ & $1.1\times10^{-4}$ & Candidate\tablenotemark{a}  \\
201549860.01 & $0.18$ &  - & $7.5\times10^{-3}$ & $0.014$ & $0.011$ & $0.22$ & $0.032$ & Candidate  \\
 \color{red} 201555883.01  & \color{red}  $0.94$  & \color{red}   -  & \color{red}  $< 10^{-4}$  & \color{red}  $< 10^{-4}$  & \color{red}  $3.6\times10^{-3}$  & \color{red}  $0.10$  & \color{red}  $3.6\times10^{-3}$  & \color{red}  FP\tablenotemark{b} \\
201565013.01 & $1.69$ &  - & $0.460$ & $0.391$ & $0.035$ & $0.06$ & $0.887$ & Candidate  \\
 \color{red} 201569483.01  & \color{red}  $2.06$  & \color{red}   -  & \color{red}  $0.437$  & \color{red}  $0.562$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.999$  & \color{red}  FP \\
201577035.01 & $0.14$ &  Y & $3.0\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.07$ & $3.6\times10^{-4}$ & Planet  \\
201596316.01 & $0.45$ &  - & $0.017$ & $< 10^{-4}$ & $3.4\times10^{-4}$ & $0.20$ & $0.017$ & Candidate  \\
201613023.01 & $0.08$ &  Y & $9.8\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.20$ & $9.8\times10^{-4}$ & Planet  \\
201617985.01 & $0.27$ &  - & $0.166$ & $< 10^{-4}$ & $0.053$ & $0.19$ & $0.219$ & Candidate  \\
201629650.01 & $0.43$ &  - & $1.5\times10^{-3}$ & $< 10^{-4}$ & $2.6\times10^{-4}$ & $0.18$ & $1.8\times10^{-3}$ & Planet  \\
201635569.01 & $0.79$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $0.043$ & $0.06$ & $0.043$ & Candidate  \\
 \color{red} 201649426.01  & \color{red}  $3.10$  & \color{red}   -  & \color{red}  $0.856$  & \color{red}  $0.142$  & \color{red}  $1.6\times10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.998$  & \color{red}  FP \\
201702477.01 & $0.70$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $4.0\times10^{-3}$ & $0.06$ & $4.0\times10^{-3}$ & Planet  \\
201736247.01 & $0.42$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $4.6\times10^{-4}$ & $0.18$ & $4.9\times10^{-4}$ & Planet  \\
201754305.01 & $0.65$ &  - & $2.5\times10^{-3}$ & $< 10^{-4}$ & $3.2\times10^{-3}$ & $0.21$ & $5.7\times10^{-3}$ & Planet  \\
201754305.02 & $0.38$ &  - & $1.9\times10^{-3}$ & $< 10^{-4}$ & $1.7\times10^{-3}$ & $0.22$ & $3.6\times10^{-3}$ & Planet  \\
 \color{red} 201779067.01  & \color{red}  $1.97$  & \color{red}   -  & \color{red}  $0.935$  & \color{red}  $0.063$  & \color{red}  $3.2\times10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.998$  & \color{red}  FP \\
201828749.01 & $0.39$ &  Y & $2.6\times10^{-3}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.17$ & $2.6\times10^{-3}$ & Candidate\tablenotemark{a}  \\

@@

201912552.01 & $0.47$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.21$ & $< 10^{-4}$ & Planet  \\
 \color{red} 201929294.01  & \color{red}  $3.12$  & \color{red}   -  & \color{red}  $< 10^{-4}$  & \color{red}  $< 10^{-4}$  & \color{red}  $2.8\times10^{-4}$  & \color{red}  $0.07$  & \color{red}  $2.9\times10^{-4}$  & \color{red}  FP\tablenotemark{b}

>>>>

201208431.01 & $0.51$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $5.7\times10^{-4}$ & $0.21$ & $5.7\times10^{-4}$ & Planet  \\
 \color{red} 201257461.01  & \color{red}  $0.59$  & \color{red}   -  & \color{red}  $< 10^{-4}$  & \color{red}  $< 10^{-4}$  & \color{red}  $1.000$  & \color{red}  $0.17$  & \color{red}  $1.000$  & \color{red}  FP \\

@@

201338508.01 & $0.63$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $2.0\times10^{-3}$ & $0.21$ & $2.0\times10^{-3}$ & Planet  \\
201338508.02 & $0.33$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $2.0\times10^{-4}$ & $0.22$ & $2.0\times10^{-4}$ & Planet  \\
201367065.01 & $0.15$ &  - & $1.0\times10^{-4}$ & $< 10^{-4}$ & $0.026$ & $0.07$ & $0.026$ & Planet\tablenotemark{c}  \\
201367065.02 & $0.67$ &  - & $0.239$ & $< 10^{-4}$ & $4.9\times10^{-3}$ & $0.17$ & $0.244$ & Planet\tablenotemark{c}  \\
201384232.01 & $0.44$ &  - & $1.0\times10^{-3}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.16$ & $1.0\times10^{-3}$ & Planet  \\
201393098.01 & $0.52$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $7.0\times10^{-4}$ & $0.19$ & $7.4\times10^{-4}$ & Planet  \\

@@

201445392.01 & $0.26$ &  - & $0.023$ & $< 10^{-4}$ & $2.5\times10^{-3}$ & $0.19$ & $0.025$ & Candidate  \\
201445392.02 & $0.18$ &  - & $0.024$ & $< 10^{-4}$ & $0.042$ & $0.21$ & $0.066$ & Candidate  \\
201465501.01 & $0.68$ &  - & $0.569$ & $< 10^{-4}$ & $2.7\times10^{-3}$ & $0.20$ & $0.571$ & Candidate  \\
201505350.01 & $2.69$ &  - & $0.088$ & $< 10^{-4}$ & $0.059$ & $0.07$ & $0.147$ & Planet\tablenotemark{d}  \\
201505350.02 & $0.70$ &  - & $4.9\times10^{-3}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.08$ & $4.9\times10^{-3}$ & Planet\tablenotemark{d}  \\
201546283.01 & $0.15$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.06$ & $< 10^{-4}$ & Candidate\tablenotemark{a}  \\
201549860.01 & $0.18$ &  - & $3.8\times10^{-3}$ & $< 10^{-4}$ & $2.1\times10^{-3}$ & $0.22$ & $5.9\times10^{-3}$ & Candidate\tablenotemark{a}  \\
 \color{red} 201555883.01  & \color{red}  $0.94$  & \color{red}   -  & \color{red}  $< 10^{-4}$  & \color{red}  $< 10^{-4}$  & \color{red}  $1.6\times10^{-3}$  & \color{red}  $0.10$  & \color{red}  $1.6\times10^{-3}$  & \color{red}  FP\tablenotemark{b} \\
201565013.01 & $1.69$ &  - & $0.639$ & $0.250$ & $6.0\times10^{-3}$ & $0.06$ & $0.895$ & Candidate  \\
 \color{red} 201569483.01  & \color{red}  $2.06$  & \color{red}   -  & \color{red}  $0.946$  & \color{red}  $0.051$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.997$  & \color{red}  FP \\
201577035.01 & $0.14$ &  Y & $2.8\times10^{-3}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.07$ & $2.8\times10^{-3}$ & Planet  \\
201596316.01 & $0.45$ &  - & $< 10^{-4}$ & $1.5\times10^{-3}$ & $2.5\times10^{-4}$ & $0.20$ & $1.8\times10^{-3}$ & Planet  \\
201613023.01 & $0.08$ &  Y & $1.0\times10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.20$ & $1.1\times10^{-4}$ & Planet  \\
201617985.01 & $0.27$ &  - & $7.6\times10^{-4}$ & $< 10^{-4}$ & $0.013$ & $0.19$ & $0.014$ & Candidate  \\
201629650.01 & $0.43$ &  - & $2.9\times10^{-4}$ & $< 10^{-4}$ & $1.8\times10^{-4}$ & $0.18$ & $4.8\times10^{-4}$ & Planet  \\
201635569.01 & $0.79$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $0.014$ & $0.06$ & $0.014$ & Candidate  \\
 \color{red} 201649426.01  & \color{red}  $3.10$  & \color{red}   -  & \color{red}  $0.797$  & \color{red}  $0.201$  & \color{red}  $1.1\times10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.998$  & \color{red}  FP \\
201702477.01 & $0.70$ &  - & $< 10^{-4}$ & $2.1\times10^{-4}$ & $2.3\times10^{-3}$ & $0.06$ & $2.6\times10^{-3}$ & Planet  \\
201736247.01 & $0.42$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $2.1\times10^{-4}$ & $0.18$ & $2.1\times10^{-4}$ & Planet  \\
201754305.01 & $0.65$ &  - & $8.4\times10^{-4}$ & $< 10^{-4}$ & $1.7\times10^{-3}$ & $0.21$ & $2.5\times10^{-3}$ & Planet  \\
201754305.02 & $0.38$ &  - & $5.5\times10^{-3}$ & $< 10^{-4}$ & $1.0\times10^{-3}$ & $0.21$ & $6.5\times10^{-3}$ & Planet  \\
 \color{red} 201779067.01  & \color{red}  $1.97$  & \color{red}   -  & \color{red}  $0.886$  & \color{red}  $0.103$  & \color{red}  $6.4\times10^{-4}$  & \color{red}  $0.00$  & \color{red}  $0.990$  & \color{red}  FP \\
201828749.01 & $0.39$ &  Y & $0.013$ & $< 10^{-4}$ & $2.2\times10^{-4}$ & $0.17$ & $0.014$ & Candidate  \\

@@

201912552.01 & $0.47$ &  Y & $< 10^{-4}$ & $2.4\times10^{-4}$ & $< 10^{-4}$ & $0.21$ & $2.5\times10^{-4}$ & Planet  \\
 \color{red} 201929294.01  & \color{red}  $3.12$  & \color{red}   -  & \color{red}  $0.700$  & \color{red}  $< 10^{-4}$  & \color{red}  $2.0\times10^{-3}$  & \color{red}  $0.07$  & \color{red}  $0.702$  & \color{red}  FP\tablenotemark{b}
